Spin canonical divisors of log stacky curves

### 2015-06-22 stacky_write_up/spin_cring.tex
add example

\begin{example}
Here we demonstrate, in detail, that case (b) ($\sigma_2 =
(0; 3, 5, 9; 0), J_2 = \{3\}$) satisfies the conditions.
\end{example}

>>>>

\begin{example}
Here we demonstrate, in detail, that case (b) ($\sigma_2 =
(0; 3, 7, 7; 0), J_2 = \{3, 4\}$) satisfies the conditions.
We have that $K_{\sx'} \sim -(\infty) + \frac{1}{3} P_1 + \frac{3}{7}
P_2 + \frac{3}{7} P_3$ for some points $P_i \neq \infty$.
We exhibit a (minimal) presentation for $R'$.

Notice that $\deg \lfloor d K_{\sx'} = -d + \lfloor \frac{d}{3}
\rfloor + 2 \lfloor \frac{3d}{7} \rfloor$.

By Max Noether's theorem over $\BP^1$ (see Lemma 3.1.1 of Voight
and Zureick-Brown \cite{vzb:stacky}),

\[
	H^0 (\sx', \lfloor 21 K_{\sx'} \rfloor) \otimes H^0 (\sx', \lfloor
	(d - 21) K_{\sx'} \rfloor) \twoheadrightarrow = H^0 (\sx', \lfloor
	d K_{\sx'} \rfloor)
\]

\noindent
is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
\geq 0$. Also, $\sigma_2$ has saturation $s = 5$ as noted in
Subsection ~\ref{ssec:g_0_saturation}. Thus, $R'$ is generated up to
degree $21 + (s - 1) = 24$.

For $d = 0, 1, 2, \ldots$ we have

\[
	dim H^0 (\sx', d K_{\sx'}) = 1, 0, 0, 1, 0, 1, 1, 2, 1, 1, 2, 1, 3, 2, 3, \ldots
\]

\noindent
so $R'$ must have some generators $x_{1, 3}, x_{1, 5}, x_{1, 7},
x_{1, 7}$. Let $(-ord_{P_1}(x_j), -ord_{P_2}(x_j), -ord_{P_3}(x_j))$
represent the pole orders of $x_i$ at each point. Then these generators
must have pole orders $(1, 1, 1), (1, 2, 2), (2, 3, 2), (2, 2, 3)$
respectively.

\end{example}
